Visual Diagnostics of a Model Explainer -- Tools for the Assessment of LIME Explanations

### 2020-09-14 paper.Rnw
updated paper after changing data
added the link for installing bullextrctr for future reference

# Load packages
library(Cairo)
library(caret)
library(cowplot)
library(dplyr)
library(forcats)
library(ggforce)
library(ggplot2)
library(ggpcp) #remotes::install_github("yaweige/ggpcp")
library(glmnet)
library(gower)
library(graphics)
library(gretchenalbrecht) #remotes::install_github("dicook/gretchenalbrecht")
library(latex2exp)
library(lime) #remotes::install_github("goodekat/lime")
library(limeaid) #remotes::install_github("goodekat/limeaid")
library(magick)
library(purrr)
library(randomForest)
library(stringr)
library(tidyr)

@@

# Add a variable to the training data with the random forest probability
# in support of a match
bullet_train$rfscore <- 
  bulletxtrctr::rtrees %>%
  predict(bullet_train %>% select(all_of(bullet_features)), type = "prob") %>%
  data.frame() %>%
  pull(TRUE.)

>>>>

# Load packages
library(bulletxtrctr) #remotes::install_github("heike/bulletxtrctr")
library(Cairo)
library(caret)
library(cowplot)
library(dplyr)
library(forcats)
library(ggforce)
library(ggplot2)
library(ggpcp) #remotes::install_github("yaweige/ggpcp")
library(glmnet)
library(gower)
library(graphics)
library(gretchenalbrecht) #remotes::install_github("dicook/gretchenalbrecht")
library(latex2exp)
library(lime) #remotes::install_github("goodekat/lime")
library(limeaid) #remotes::install_github("goodekat/limeaid")
library(magick)
library(purrr)
library(randomForest)
library(stringr)
library(tidyr)

@@
